---
title: "Hello hw09"
author: "antonyagonzalez"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

##Package Description

The purpose of this mini package is to make life easier when dealing with long tedious regression output and get what you need from it. Eventually, this package will become a larger, more useful package with many extraction functions.

In the examples below, I will work with the iris data to show you what the functions in this package do. NOTE: I have not standardized the variables below, so the resulting betas will not be correctly standardized.

```{r}
library(hw09)
library(dplyr)
```



##Extract information for a three-way interaction

NOTE: This function will only work if you have 3 predictors or more in your model, and only up to a three-way interaction. Four-way interactions are a terrible idea anyway, don't do them.

Let's say I am running a regression model with a predicted three-way interaction between petal length, petal width, and sepal width predicting sepal length. After standardizing the variables of interest, I would use the linear model below.

```{r}
example <- lm(formula = Sepal.Length ~ Petal.Length * Petal.Width * Sepal.Width, data = iris)
```

Normally the summary output would be as follows:

```{r}
summary(example)
```

But that's a lot of information to look through, and can be kind of a headache when trying to write up a paper. What if all I care about is knowing the information about the three-way interaction?

Instead of the summary, I will use interact3(). It will even give me the confidence intervals for the regression coefficient as well.

```{r}
interact3(example)
```

Much easier to read and work with.

##Extract information for the interaction between predictors 1 & 2.

Now let's say I am working with the same model as above, but at the moment, I really only care about whether or not there is an interaction between petal length and petal width predicting sepal length.

This is where I would use interact12()

```{r}
interact12(example)
```

##Meta-analyzing standard regression coefficients

The third (and final, for now) function in this package meta-analyzes standardized regression coefficients that you input by hand.

Let's say I only cared about the setosa and versicolor species, and wanted to conduct a meta-analysis of the relationship between petal length, petal width, and sepal width predicting sepal length for those two species.

```{r}
setosa <- filter(iris, Species == "setosa")
setosa_model <- lm(formula = Sepal.Length ~ Petal.Length * Petal.Width * Sepal.Width, data = setosa)

versicolor <- filter(iris, Species == "versicolor")
versicolor_model <- lm(formula = Sepal.Length ~ Petal.Length * Petal.Width * Sepal.Width, data = versicolor)
```

First, I will extract the betas I care about.

```{r}
interact3(setosa_model)

interact3(versicolor_model)
```

Now, I will meta-analyze them.


```{r}
metabeta(b1 = 5.42, se1 = 6.23, b2 = 1.18, se2 = 2.20)
```

Another shortcut to doing this is below:

```{r}
setosa_beta <- interact3(setosa_model)
versicolor_beta <- interact3(versicolor_model)

metabeta(b1 = setosa_beta[[1]], se1 = setosa_beta[[2]], b2 = versicolor_beta[[1]], se2 = versicolor_beta[[2]])
```

